Meta-analysis

### 2020-02-14 05_MetaAnalysis.Rmd
Adding more explaination to the analysis

```{r LM_AUDPC}
library(MuMIn)
summary(lm(grain_yield.t.ha ~ AUDPC_m, data = slimmer_PM_dat))
summary(lm(grain_yield.t.ha ~ AUDPS_m, data = slimmer_PM_dat))
```

Area under the disease progress stairs (AUDPS) shows almost the same fit as the AUDPC linear model.

@@

AUDPC becomes a significant predictor of grain yield when the random effect `trial` is accounted for. However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial. Lets see if the model improves when AUDPC is used as a random slope for trial.

@@

```{r AUDPCvsAUPDS}
r.squaredGLMM(Me_mod2.s)
r.squaredGLMM(Me_mod2)
```

The R-squared of the AUDPC model is a better fit compared to the AUDPS model. From here on we will use AUDPC

@@

summary(Me_mod4)

@@

Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC. In fact a model comparison shows AUDPC is significantly better at predicting grain yield.   
We shall proceed by including the spray management predictor into the analysis.  
First lets assess the `spray_management` variable as an additive fixed effect.

@@

Also there is no reason to include these terms individually in the model to assess their independant effect on grain yield as we know the application of fungicide to mitigate yield loss is aimed at reducing the disease in the crop.

@@

anova(Me_mod5, Me_mod6)
```
As we would hope this improves out model again. Not only do we want to know how much spray_management moderates the effect disease (AUDPC) on yield. We might also want to know on average what effect did each of the spray management have on yield.

```{r AUDPCplusspraymangement}
Me_mod7 <- lmer(grain_yield.t.ha ~ AUDPC_m : spray_management+ spray_management + (AUDPC_m|trial),
              data = slimmer_PM_dat)

anova(Me_mod6, Me_mod7)
```
The model with an additive spray_management term did not significantly improve the model, however we don't need the term in the model to answer our hypothesis. We can still determine the effect of spray_management on yields through the interactive AUDPC:spray_management term.

@@

anova(Me_mod6, Me_mod8)
```
As expected the model produced an error warning theat the maximum number of evaluations were exceeded. Also the model comparisons show that the newer Me_mod7 was not a better model. We we proceed with Me_mod6 as the model with the best fit.

```{r LMER_AUDPC2_results}
summary(Me_mod6)
coef(Me_mod6)[["trial"]][
   order(coef(Me_mod6)[["trial"]]$AUDPC_m),]
```
The first output shows our random effects do a good job of explaining the variation leaving less residual variation than what is explained by the random intercept, trial.  
In the fixed effects the intercept gives an estimate of the average yield across all treatments. The other fixed effects show the change in predicted yield as AUDPC increases under each of the spray_management factors. Spray_management treatments, control, Early, and recommended show significant declines in grain_yields as AUDPC increases. Recommended_plus and Late_plus show no significant decline in grain yield as AUDPC increases.

Here the intercept represents an estimate of the trial yield without the limitation of the disease. AUDPC_m shows the slope of the regression for grain yield as AUDPC increases. The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope. In other words higher yielding mungbean crops were likely to see greater losses from disease.

@@

```{r LM_AUDPC}
summary(lm(grain_yield.t.ha ~ AUDPC_m, data = slimmer_PM_dat))

Area under the disease progress curve (AUDPC) shows no linear relationship with the grain yield data when analysed without respect to any other factor. Lets use a mixed effect model which incorporates `trial` as a random effect. This makes sense given when we plotted the data subset by trial we could see a better relationship between grain yield and AUDPC.

```{r LMER_AUDPC1}
Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
              data = slimmer_PM_dat)
summary(Me_mod1)
```

AUDPC becomes a significant predictor of grain yield when the random effect `trial` is accounted for. However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial. Lets see if the model improves when AUDPC is used as a random slope for trial.

```
The model is significantly improved, lower AIC and a higher log likelihood.

```{r LMER_AUDPC2_results}
summary(Me_mod2)
coef(Me_mod2)[["trial"]][
   order(coef(Me_mod2)[["trial"]]$AUDPC_m),]
```
Here the intercept represents an estimate of the trial yield without the limitation of the disease. AUDPC_m shows the slope of the regression for grain yield as AUDPC increases. The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope. In other words higher yielding mungbean crops were likely to see greater losses from disease.

Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1|trial),
              data = slimmer_PM_dat)
summary(Me_mod3)

Me_mod4 <- lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity|trial),
              data = slimmer_PM_dat)
summary(Me_mod4)

anova(Me_mod3, Me_mod4)

Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC.

We shall proceed by including the spray management predictor into the analysis.

Me_mod6 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
              data = slimmer_PM_dat)
summary(Me_mod6)
anova(Me_mod2, Me_mod5)
anova(Me_mod5, Me_mod6)

Me_mod7 <- lmer(grain_yield.t.ha ~  AUDPC_m : spray_management+ (AUDPC_m|trial),
              data = slimmer_PM_dat)

>>>>

## AUPDC and PM severity meta-analysis
Now it's time to look at how the spray managment scenarios might impact disease pressure on the mungbean yields. First lets evaulate which measure of disease is the most robust predictor for yield loss, AUDPC, AUDPS or disease incidence at the end of the season.  
```{r LM_AUDPC}
library(MuMIn)
summary(lm(grain_yield.t.ha ~ AUDPC_m, data = slimmer_PM_dat))
summary(lm(grain_yield.t.ha ~ AUDPS_m, data = slimmer_PM_dat))
```

Area under the disease progress stairs (AUDPS) shows almost the same fit as the AUDPC linear model. AUDPC and AUDPS are not good predictors of loss in yield overall, without the inclusion of a `trial` parameter. Lets test the model with the inclusion of `trial` as a random effect.

@@

AUDPC becomes a significant predictor of grain yield when the random effect when accounting for `trial`. However we noticed in the plots earlier that not only the intercept but the slope varies depending on the trial. Lets see if the model improves when AUDPC is used as a random slope for trial.

@@

```{r AUDPCvsAUPDS}
r.squaredGLMM(Me_mod2.s) # Rsquared for AUDPStairs
r.squaredGLMM(Me_mod2)# Rsquared for AUDPCurve
```

The R-squared of the AUDPC model is a better fit compared to the AUDPS model.  
> From here on we will use AUDPC.

@@

summary(Me_mod4)
r.squaredGLMM(Me_mod4)

@@

Powdery mildew incidence at the end of the season was a significant covariate for grain yield, however was a weeker predictor compared to AUDPC. In addition model comparison shows AUDPC is significantly better at predicting grain yield.  
### Spray management and AUDPC
We shall proceed by including the spray management predictor into the analysis.  
First lets assess the `spray_management` variable as an additive fixed effect.

@@

It is also worth noting there is no reason to include these parameters individually in the model to assess their independant effect on grain yield as we know the application of fungicide to mitigate yield loss is aimed at reducing the disease in the crop.

@@

anova(Me_mod5, Me_mod6)
```

@@

anova(Me_mod6, Me_mod8)
```
As expected the model produced an error warning stating the maximum number of evaluations were exceeded. Also the model comparisons show that the newer Me_mod7 was not a better model. We we proceed with Me_mod6 as the model with the best fit.

```{r LMER_AUDPC2_results}
summary(Me_mod6)
coef(Me_mod6)[["trial"]][
   order(coef(Me_mod6)[["trial"]]$AUDPC_m),]
```
The first output shows our random effects do a good job of explaining the variation leaving less residual variation than what is explained by the random intercept, trial.  
In the fixed effects the intercept gives an estimate of the average yield across all treatments (1.29 t/Ha). The other fixed effects show the change in predicted yield as AUDPC increases under each of the spray_management factors. Spray_management treatments, control, Early, and recommended show significant declines in grain_yields as AUDPC increases. Recommended_plus and Late_plus show no significant decline in grain yield as AUDPC increases.

The second output is the random effect coeficients. Here the intercept represents a yield estimate for each trial without the limitation of the disease. AUDPC_m shows the slope of the regression for grain yield as AUDPC increases. The coefficients of the model (ordered by AUDPC) show that higher yielding trials had a steeper negative slope. In other words higher yielding mungbean crops were likely to see greater losses from disease.

@@
